\documentstyle[11pt]{article}
\voffset=-1.2in
\hoffset=-0.9in
\setlength{\textheight}{10.750in}
\setlength{\textwidth}{7.1in}
\baselineskip=1in
\begin{document}
\begin{center}
 {\Large    WILSON ENRIQUEZ}
\\
{\scriptsize Escuela Superior Politecnica del Litoral,\\
851 S. Morgan (M/C 249) Chicago, Illinois 60607-7045\\
(312) 996-3041, goetz@babe.math.uic.edu\\  http://www.math.uic.edu/$\sim$goetz/\\}
\end{center}


 
\hspace{-.29in}
 {\bf  EDUCATION }
\vspace{-.09in}
 \begin{list}{name}{\labelwidth 18em \leftmargin .93in \itemsep -.025in }

\item [\bf 1996] {\bf PhD in  Mathematics} (expected May 1996)
\begin{itemize}
\vspace{-.04in}
\item  {\bf  Thesis:} {\em Dynamics of Piecewise Isometries}, University of Illinois at Chicago. 
\hspace{-.29in}
\vspace{-.04in}
 \item {\bf  Advisor:} Steven Hurder


\end{itemize} 
 \item [\bf 1992] {\bf MS in  Mathematics} from the University of Illinois at Chicago. 
 \item  [\bf 1991]  Summer Student at the National Science  and   
                     Research Geometry Center, \vspace{-.032in} \\  mathematics undergraduate at the University of Illinois at Chicago. 
\item   [\bf 1989-90]  Student  of  Physics and Mathematics at  Wroclaw University (Poland).
\end{list}
\vspace {.16in}

 \hspace{-.29in}
{\bf  HONORS and DISTINCTIONS}  
\begin{itemize}

\item {\bf Talks at Conferences} (complete list on the second page)
\begin{itemize}
\vspace{-.09in}
\item  {\it Geometry and Dynamics } (Warsaw, June 1995)
\vspace{-.09in}

\item {\it Dynamics and Foliations } (Warsaw, May 1995)
\vspace{-.09in}
\item  {\it North East Dynamics Conference } (Stony Brook, April 1994)
\vspace{-.09in}
\item {\it AMS Special Sessions }:  
(Stillwater, October 1994); (Orlando, March 1995); \\(Orlando, January 1996); (Baton Rouge, April 1996)
\end{itemize}

\item \vspace{-.04in}{\bf  Seminars and Colloquia}
\begin{itemize}
\vspace{-.06in}
\item Northwestern University (November 1995) 
\vspace{-.06in}
\item University of Southern California (January 1995)
\vspace{-.06in}
 \item University of Texas at Austin (October 1994)
\end{itemize}


\item {\bf Awards and Scholarships}
\begin{list}{name}{\labelwidth 8em \leftmargin 0.566in \itemsep -.025in}
\vspace{-.09in}
\item[\bf 1994-95] University of Illinois Fellowship.

\item[\bf 1991-94] United States Department of Education Graduate Fellowship. 
    

\end{list} 

\end{itemize}

\vspace {.16in}

 {\bf \hspace{-0.29in}  TEACHING EXPERIENCE: INNOVATIVE FORMS AND USE OF TECHNOLOGY}
\vspace{-.001in}
\begin{itemize}
\item \vspace{-0.099in} {\bf Instructor}, Multivariable Calculus, (anticipated Spring 1996) 
\item \vspace{-0.099in} {\bf Teaching Assistant Consultant \&  Training} (August 1995)
\begin{itemize}
\vspace{-.1in}
\item Conducted a series of discussions addressing issues on quality teaching.

\end{itemize} 
\item \vspace{-0.099in} {\bf Teaching Assistant}, Emerging Scholars Program (Fall 1995) 
\begin{itemize}
\vspace{-.1in}
\item Supervised and coordinated cooperative learning of multivariable calculus students.
\vspace{-0.077in}
\item Introduced students to utilizing computer software for graphing  and visualizing   \\ three-dimensional objects.

\end{itemize} 



\item \vspace{-0.099in} {\bf Teaching Assistant} (Spring 1995).
\begin{itemize}
\vspace{-0.099in}
\item  Calculus II (discussion leader). 
\vspace{-0.077in}
\item Participated in the Mathematics Tutoring Lab 
\end{itemize}
\item \vspace{-0.099in} {\bf Teaching Assistant}  (Fall 1994) 
\begin{itemize}
\vspace{-0.099in}
\item Honors Calculus (discussion leader).
\vspace{-0.077in}
\item  Utilized Maple on NeXTStep workstations. 
\end{itemize}
\item \vspace{-0.099in} {\bf Computer Assistant} (Spring 1994)
\begin{itemize}
\vspace{-0.099in}
\item Assisted professors in teaching courses which utilized computer software. 
\end{itemize}
\end{itemize}

\hfill  {\bf over $\searrow$}

\newpage
\voffset=-.50in

 

 \hspace{-.29in} {\bf FURTHER ACHIEVEMENTS}
\vspace{-.09in}
\begin{itemize}

\item  The top 250 score (nationwide) in the Putnam Examination  \vspace{-.032in} \\ 
                     (the highest score in the history of the UIC Math Department).
              
\item \vspace{-0.08in} Summer  undergraduate  research position  at   the 
                     National Science  and   
                     Research \vspace{-.032in}  \\  Geometry Center in Minneapolis, Minnesota. 

 \item  \vspace{ -.09in}      Participated in the National Science Foundation Geometry Institute (Park City, Utah).


         \item \vspace{ -.09in} {\bf fourth} prize in the National Mathematics Olympiad  in all of   
                Poland,
         \item \vspace{ -.09in} {\bf 14th} place in Poland in the National Physics Olympiad,
         \item \vspace{ -.09in} {\bf 18th} place in Poland in the National Olympiad in Astronomy.
             
 

\end{itemize}


\vspace{.12in}
\hspace{-.29in} {\bf  COMPUTER SCIENCE EXPERIENCE}
\begin{itemize}
\vspace{-0.09in}
\item Extensive experience with computing and visualization software in teaching mathematical courses.

\vspace{-0.09in}
\item Assistant to the system administrator of the unix NeXT lab (Spring 1994).


\vspace{-.09in} \item Co-authored the software ``Geometric Construction''\\ \vspace{-.032in}  (First International Computer Science Olympiad in former Yugoslavia). 
\vspace{-.09in}
\item  ``Mathematica'', ``Maple'', C, Pascal, Latex, WWW.
\end {itemize}


\hspace{-.29in} {\bf BACKGROUND:}
\begin{itemize}
\vspace{-.06in}
\item  President of the Mathematics Graduate Student Association (1993/1994).  \vspace{-.06in}
\item   Languages:   Polish, French, Italian, Russian.  
\vspace{-.06in}
\item Permanent Resident of the  United States. (Citizenship expected in 1996)
\end{itemize}

\vspace{.12in}
 
  \hspace{-.29in} {\bf  PUBLICATIONS and REPORTS }
\begin{itemize}
\vspace{-.08in}

\item    {\em Figure Eight Attractor},  
submitted to {\bf Ergodic Theory and Dynamical Systems.}

  \vspace{-.08in}
\item  {\em Dynamics of Piecewise Isometries},    
submitted to the {\bf Transactions of AMS.}
\vspace{-.08in}
\item    {\em The  Midpoint   Polygon  Transformation},  
{\bf National Science Foundation Center\\ for Visualization of Geometric Structure, Reports  91} - 
        Undergraduate    Research\\
Experiences,  Summer 91,  p.73.
\vspace{-.08in}
\item  { \em Constrained Isometric Walks},  in preparation.


\end{itemize}










			
\end{document}
